A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-09-29 paper.tex
Rephrase and fix grammar

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics are complicated in subscription services, therefore, we illustrated the challenges in this section. As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. However, issues such as consumers can only initiate a refund after getting the data or in a certain time period, the broker should host and set a vote timeline to count the votes, and handling the condition that not enough consumers join the vote need to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fee, which is a deal between brokers and providers. If they can not reach a consensus of the brokerage fee during the subscription period, brokers can launch a refund and refuse to handle the product. Third, the refund could launch by providers when they fail to maintain products as committed.

@@

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
\subsubsection{Experiment}
According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message. The result directs a way to improve MAM. Applying remote PoW greatly reduces the elapsed time, then channel creation is the next primary barrier that should be removed. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA, respectively.

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much flatter than the result of MAM which ensures E2EE can consistently perform in an acceptable time range. Under our design which delegates MAM operations with Accel and the presented E2EE protocol, the data providers can include resource-constrained hardware into the data subscription economy. E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.

>>>>

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics are complicated in subscription services; therefore, we illustrate the challenges in this section. As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. It is notable that consumers can only initiate a refund after getting the data or in a certain time period. In this situation, the broker should host and set a vote timeline to count the votes, as well as handling the condition that not enough consumers join the vote. The process needs to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fees, which is a deal between brokers and providers. If they cannot reach a consensus on the brokerage fee during the subscription period, brokers can launch a refund and reject to handle the product. Third, the refund could be launched by providers when they fail to maintain products as committed.

@@

\subsection{MAM vs. the delegated MAM}
\label{section:smart_contract_evaluation}
\subsubsection{Experiment}
According to Fig.\ref{fig:op_share}, PoW, sending to IOTA full node and creating a channel, these three steps take most of the time to broadcast a MAM message. The result directs a way to improve MAM. Applying remote PoW greatly reduces the elapsed time; hence, the channel creation is the next primary barrier that should be removed. With the adoption of delegated MAM and E2EE, the MAM channel creation would be delegated to Accel, which dramatically enhances the efficiency and makes MAM available for low-level devices. In this way, the performance of delegated MAM stands out from the original MAM one, particularly for different payload sizes. Elapsed time for internet communication and PoW are not included because the steps are the same after sending messages to Accel. Excluding the uniform steps allows us to compare the performance between MAM and delegated MAM clearly. In addition, the MAM channel creation and E2EE asymmetric key pair generation are not counted either, since the two operations are rarely executed. In the E2EE protocol, we respectively choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and Curve P-256 for ECDSA.

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals the elapsed time of E2EE is obviously less than the elapsing time of MAM, which shows that the previous process is a much more appropriate solution to resource-constrained systems in sending authenticated streaming data. The slope of the E2EE result is much flatter than the result of MAM, which means the former solution can consistently perform in an acceptable time range. In summary, our design enables the resource-constrained hardware to be data providers in the data subscription economy due to the efficiency of the delegated MAM operation and E2EE protocol. The new protocol ensures tamperless data transmission; meanwhile, only authorized subscribers can read the encrypted information.
